\vspace{-2cm} Inference on the Effects of Observed Features \\ in Latent Space Models for Networks

### 2017-05-06 manuscript.tex
added online appendix

We also repeat this simulation study using \texttt{amen} \citep{hoff2015dyadic, minhas2016inferential}. We omit the poisson family, and, due to the computational cost of the simulation, we consider only networks with 25 nodes or 100 nodes. Rather than constructing an omitted variable as described above, we draw from a standard normal distribution $\mathbf{u}$, and, because we are considering symmetric networks, take the outer product of $\mathbf{u}$ with itself to construct the latent factor. We take 100,000 MCMC samples after x burn-in iterations, and we assess convergence using the diagnostic of \cite{raftery1992practical}.

@@

In our repetition of this simulation with \texttt{amen} we find similar results, with the exception of type-2 error rates, which, as expected, are substantially lower for \texttt{amen}. However, type-1 error rates remain elevated, as is bias in the case where there is a latent dependence structure that is correlated with the observed covariate. \texttt{amen} does perform better in the case where it is used despite the absence of such a latent dependence structure though, relative to \texttt{latentnet}, which is to be expected given that it outperforms \texttt{latentnet} in terms of type-2 error. Again, \texttt{amen} performs well in terms of generalization error, coming close to the theoretical lower bound.

@@

>>>>

We also repeat this simulation study using \texttt{amen} \citep{hoff2015dyadic, minhas2016inferential}. We omit the poisson family, and, due to the computational cost of the simulation, we consider only networks with 25 nodes or 100 nodes. Rather than constructing an omitted variable as described above, we draw from a standard normal distribution $\mathbf{u}$, and, because we are considering symmetric networks, take the outer product of $\mathbf{u}$ with itself to construct the latent factor. We take 100,000 MCMC samples after 500 burn-in iterations, and we assess convergence using the diagnostic of \cite{raftery1992practical}.

@@

In our repetition of this simulation with \texttt{amen} we find similar results, with the exception of type-2 error rates, which, as expected, are substantially lower for \texttt{amen}. However, type-1 error rates remain elevated, as is bias in the case where there is a latent dependence structure that is correlated with the observed covariate. \texttt{amen} does perform better in the case where it is used despite the absence of such a latent dependence structure though, relative to \texttt{latentnet}, which is to be expected given that it outperforms \texttt{latentnet} in terms of type-2 error. Again, \texttt{amen} performs well in terms of generalization error, coming close to the theoretical lower bound. The results of our simulations with \texttt{amen} are available in the Online Appendix.

@@

\newpage
\section*{Online Appendix}
Below we replicate the simulation study results figures using the results from our simulation with the recently developed \texttt{amen} package. Note that these simulations exclude (1) the Poisson family, which is not available in the \texttt{amen} package, and (2) the 50-node networks, which we left out in the interest of lessening the computational burden of the simulation.
